Tina Paper In Development

### 2024-11-20 docs/writing/paper.tex
Having a hard time transitioning well into the results/discussion

\section{Results}
\subsection{Scans of Cookies and Cores}
The microscope lens greatly improved the maximum resolution of the digitization. Resolutions of up to 13,400 DPI were achieved, a large improvement when compared to 
both high resolution flatbed scanners (Epson® Perfection v750 PRO) and CaptuRING.

\subsection{Functional Limits}
With such high resolution, multiple logistics concerns arise. First is the file size. With such a high resolution, the size of the images can become extremely large. A cookie
5 inches in diameter would result in an image with 67,000 pixels squared. This easily exceeds the 2.5 GB maximum file size in a TIFF - most software for viewing the file will also 
be incompatible with any file this big as well.

\section{Discussion}
Discuss the implications of your results here.

\subsection{Strengths and Opportunities}

\subsection{Opportunities for Improvement}

\section{Conclusion}
Summarize your key findings here.

>>>>

Depending on the analysis, it is not necessary to digitize samples at a very high DPI. To address this, a parameter in the machine configuration file 
allows the user to downsize images before they get stitched together to avoid unnecessary sample detail.

\section{Results}
\subsection{Scans of Cookies and Cores}
While the theoretical maximum resolution of the system can achieve 32,000 DPI smaller resolutions were preferred in our digitizations to decrease digitization time and filesize.
This is a significant improvement when compared to the scanning resolution of flatbed scanners (Epson® Perfection v750 PRO), CaptuRING, and Gigapixel: 6,000 DPI, 4,200 DPI, and 19,812 DPI respectively.

So far we have used this machine to digitize approximately 90 tree cookies which diameter's varied between 1 to 12cm.
While the machine has a work plane of approximately 60cm x 60cm, the limiting factor of a sample is its surface area. 
This is more of a concern for cookies than for cores, as even a 60cm length core will have less surface area than a 12cm x 12cm cookie. 
See FIGURE for sample size, DPI, and filesize graph.

A strong feature between this and alternatives is the ability to setup multiple samples with their identifiers into a queue to be digitized. 
This conveniently makes interactions with the machine in bursts rather than having to time when a sample will be done to begin setting up another. 
We were able to successfully queue 10 cookie samples to be digitized although we did not stress test this further.

See FIGURE for the digitization and stitching times.

\subsection{Functional Limits}
With such high resolution, file size limitations can arise. One of the most common lossless image filetypes, TIFF, is limited to 2.5GB.
But even before we reach this limit, software such as ImageJ, CooRecorder, and other image viewers/analysis tools are not designed to handle larger filesizes nearing 2GB.
This is important to note as this machine is capable of stitching files greater than 2.5GB but the results are stored in binary NumPy memory map files rather than TIFF's. 
Storing data this way allows the user to either downsize stitched image or view portions of it with their own script.

\section{Discussion}
By taking advantage of a common 3 degree of freedom cartesian machine design, edge computing device, and a microscope camera we were able to design a cost effective and high resolution digitization tool for wood samples. 
We significantly increased the maximum sample length and maximum resolution compared to common alternatives in the field. 
In addition, the machine design was intended to be readily replicated by labs with minimal engineering experience and equipment.

\subsection{Strengths and Opportunities}
Our design has tried to minimize the barriers to building this machine in smaller labs. After investing a few hours in the sourcing and assembly of parts, 
the rest of the implementation has been completed. Digitized samples from this machine have been able to have tree rings registered onto their images using CooRecorder.
They have also been ran through a deep learning tree ring identification R-CNN model, although this took an extremely long time even with a hypercomputer.

\subsection{Opportunities for Improvement}
Integration into a cloud data storage system would be a great addition to remove the need for an operator to move the final data with a physical external drive. 
Further testing with vessel counting models is also an interesting extension to take advantage of high resolution scans of well prepared samples.

\section{Conclusion}
